A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2021-03-02 03_Yield_MetaAnalysis.Rmd
Edit headings

## metafor analysis

@@

### Influence of disease onset

@@

@@

### Influence of disease pressure

@@

@@

```{r osset_Metafor-analysis}
PM_mv_dp <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management * d_pressure,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_Y
)

@@

### Meta-analysis moderator estimates table
Let's present the meta-analysis results for the moderator variables in a table of estimates.

@@

@@

@@

Let's investigate the treatment contrasts

@@

****

@@

Now let's visualise this as a forest plot.

```{r netmeta-forest}
forest(
   net_con,
   reference.group = 1,
   rightcols = c("effect", "ci", "Pscore"),
   rightlabs = "P-Score",
   small.values = "bad"
)
```

>>>>

<br>  
<br>  
<br>

## Spray schedule meta-analysis  
### Spray schedule moderator

@@

<br>  
<br>  
<br>  
******

### Disease onset interaction with spray schedule

@@

<br>  
<br>  
<br>  
******

@@

<br>  
<br>  
<br>  
******

### Disease pressure interaction with spray schedule

@@

<br>  
<br>  
<br>  
******

#### metafor disease pressure interaction

@@

```{r Dpressure_Metafor-analysis}
PM_mv_dp <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management * d_pressure,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_Y
)

@@

<br>
<br>
<br>
******

## Meta-analysis results summary
### Moderator estimates table
Let's present the meta-analysis results for the moderator variables in a table of estimates.

@@

<br>  
<br>

@@

### Moderator estimates plot

@@

<br>  
<br>

### Moderator contrasts
Let's investigate the treatment contrasts

@@

<br>  
<br>  
<br>  
******

@@

<br>  
<br>

### netmeta estimates plot
Now let's visualise this as a forest plot.

```{r netmeta-forest}
forest(
   net_con,
   reference.group = 1,
   rightcols = c("effect", "ci", "Pscore"),
   rightlabs = "P-Score",
   small.values = "bad"
)
```
<br>  
<br>  
<br>  
******

### Moderator netgraph

### 2021-03-02 04_Severity_MetaAnalysis.Rmd
Edit headings

# Meta-analysis of powdery mildew severity

@@

@@

@@

```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   pull(Freq)

>>>>

# Powdery mildew severity Meta-analysis

@@

<br>  
<br>  
<br>  
******

## Disease severity spray schedule meta-analysis

@@

<br>  
<br>  
<br>

### Disease severity moderator contrasts

@@

<br>  
<br>  
<br>

### Meta-analysis summary table
```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   pull(Freq)

### 2021-03-02 index.Rmd
Edit headings

## Contents
This compendium is broken down into seven sections:

   1. [Details of the experiments, and application of inclusion criteria in the analysis][Trials considered for inclusion in meta-analysis]  
      a. [Inclusion criteria][Criteria for inclusion in meta-analysis]
      b. [Import data][Import data]
      c. [Trial summary][Summary of all trials]
      d. [Locations of considered trials][Experiment locations]
      e. [Apply selection criteria][Subset data to selection criteria]
      f. [Classifing moderator variable - spray schedule][Classifying spray schedule]
      g. [Identifing treatment variance][Identify variance]
   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
      a. [Fungicides][Fungicides]  
      b. [Mungbean cultivar][Mungbean cultivars]  
      c. [Row spacing][Row spacing]  
      d. [Rainfall][Yield vs in-season rain]  
      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
   6. [Manuscript Wireframe][Manuscript wire frame]
   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]

>>>>

## Contents
This compendium is broken down into four sections:

   1. [Details of the experiments, and application of inclusion criteria in the analysis][Trials considered for inclusion in meta-analysis]  
      a. [Inclusion criteria][Criteria for inclusion in meta-analysis]
      b. [Import data][Import data]
      c. [Trial summary][Summary of all trials]
      d. [Locations of considered trials][Experiment locations]
      e. [Apply selection criteria][Subset data to selection criteria]
      f. [Classifing moderator variable - spray schedule][Defining spray schedule variable]
      g. [Identifing treatment variance][Identify variance]
   2. [Preliminary data exploration][Preliminary Analysis]  
      a. [Trial summary statistics]  
         i) [Seasons][Trial seasons]  
         ii) [Location][Trial locations]  
         iii) [Severity and Yield summary table][Powdery mildew severity and mungbean grain yield summary per trial]  
         iv) [Severity and Yield summary plots][Summary plots]  
      b. [Treatment focused summaries]  
         i) [Fungicide type]  
         ii) [Fungicide doses]  
         iii) [Number of fungicide sprays]  
         iv) [Mungbean cultivars]  
         v) [Row spacing]  
         vi) [Disease pressure]  
         vii) [In-crop rainfall]  
   3. [Grain yield meta-analysis]  
      a. [Spray schedule meta-analysis and moderator interactions][Spray schedule meta-analysis]  
         i. [Spray schedule moderator]  
         ii. [Disease onset interaction with spray schedule]
         iii. [Disease pressure interaction with spray schedule]  
         iv. [Compare variance-covavriance matrix structure][Test variance-covavriance matrix structure]  
      b. [Meta-analysis results summary]  
         i. [Moderator estimates table]  
         ii. [Moderator estimates plot]  
         iii. [Moderator contrasts]  
         iv. [Profile plots]
      c. [netmeta analysis]  
         i. [netmeta estimates plot]
         ii. [Moderator netgraph]
   4. [Powdery mildew severity Meta-analysis]  
      a. [Disease severity spray schedule meta-analysis]

      a. [Fungicides][Fungicides]  
      b. [Mungbean cultivar][Mungbean cultivars]  
      c. [Row spacing][Row spacing]  
      d. [Rainfall][Yield vs in-season rain]  
      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
   6. [Manuscript Wireframe][Manuscript wire frame]
   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]
